Beyond Adaptive Web Design

### 2014-02-20 paper/paper.tex
refactor(paper): refactor build
refactor: restyle sentences

% Please do not remove the following commands:
\editpages{1}{8}

@@

We consider ``adaptive web design'' as a equal to creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access sensors in devices and use them to enhance user experience.

@@

\subsection{Touch} % (fold)
\label{sub:touch}

@@

% subsection touch (end)

\subsection{Speech} % (fold)
\label{sub:speech}

@@

% subsection speech (end)

\subsection{Device motion} % (fold)
\label{sub:device_motion}

@@

% subsection device_motion (end)

\subsection{Video Motion} % (fold)
\label{sub:video_motion}

@@

% subsection video_motion (end)

@@

\subsubsection{Voice commands} % (fold)
\label{ssub:voice_commands}

@@

% subsubsection voice_commands (end)

\subsubsection{Gyroscope rotation} % (fold)
\label{ssub:gyroscope_rotation}

@@

\begin{figure}[h]
    \begin{center}
        \includegraphics[width=0.25\textwidth]{../images/gyroscope}
        \caption{Scrolling in the webpage by gyroscope}
        \label{fig:gyroscope}
    \end{center}
\end{figure}

@@

% subsubsection gyroscope_rotation (end)

\subsubsection{Video camera motion} % (fold)
\label{ssub:video_camera_motion}

Almost every moder device contains a video camera. This is a great opportunity to introduce video motion to web applications. We can control web sites using motion gestures.

We use a video camera stream and devide it into image frames. Then we can detect a website user in the each frame using a hsv filter. When we compare all pixels in two adjacent frames we get difference points. When we apply this comparision to multiple frames we can calculate a motion vector.

\begin{figure}[h]
    \begin{center}
        \includegraphics[width=0.75\textwidth]{../images/videomotion}
        \caption{Converting video stream into motion vector}
        \label{fig:videomotion}
    \end{center}
\end{figure}

@@

% subsubsection video_camera_motion (end)

@@

There are a lot of commonly used web services that produce unnecessary traffic. Elements like videos or maps are a common part of the most web sites. All of them produces many requests and the web traffic even the website user doesn't want to watch the video or browse the map. There are also native mobile application for that services with better perfomance. So what can we to do? This is actually a great opportunity to utilize conditional loading to serve the best experience for the right context.

@@

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.62\textwidth]{../images/maps.png}
        \caption{Maps component}
        \label{fig:maps}
    \end{center}
\end{figure}

>>>>

% Please do not remove the following commands:
\editpages{1}{8}
\hyphenation{pha-blets}

@@

We consider ``adaptive web design'' as an equal with creating a single Web experience that adjusts based on the capabilities of the device and browser. Website can access sensors in devices and use them to enhance user experience.

@@

\paragraph{Touch} % (fold)
\label{sub:touch}

@@

% paragraph touch (end)

\paragraph{Speech} % (fold)
\label{sub:speech}

@@

% paragraph speech (end)

\paragraph{Device motion} % (fold)
\label{sub:device_motion}

@@

% paragraph device_motion (end)

\paragraph{Video Motion} % (fold)
\label{sub:video_motion}

@@

% paragraph video_motion (end)

@@

\paragraph{Voice commands} % (fold)
\label{ssub:voice_commands}

@@

% paragraph voice_commands (end)

\paragraph{Gyroscope rotation} % (fold)
\label{ssub:gyroscope_rotation}

@@

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.2\textwidth]{../images/gyroscope}
        \caption{Scrolling in the webpage by gyroscope}
        \label{fig:gyroscope}
    \end{center}
\end{figure}

@@

% paragraph gyroscope_rotation (end)

\paragraph{Video camera motion} % (fold)
\label{ssub:video_camera_motion}

Almost every moder device contains a video camera. This is a great opportunity to introduce video motion to web applications. We can control web sites using motion gestures. We use a video camera stream and devide it into image frames. Then we can detect a website user in the each frame using a hsv filter. When we compare all pixels in two adjacent frames we get difference points. When we apply this comparision to multiple frames we can calculate a motion vector.

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.7\textwidth]{../images/videomotion}
        \caption{Converting video stream into motion vector}
        \label{fig:videomotion}
    \end{center}
\end{figure}

@@

% paragraph video_camera_motion (end)

@@

There are a lot of commonly used web services that produce unnecessary traffic. Elements like videos or maps are a common part of the most web sites. All of them produces many requests and the web traffic even the website user doesn't want to watch the video or browse the map. There are also native mobile application for that services with better perfomance. So what can we to do? This is a great opportunity to utilize conditional loading to serve the best experience for the right context.

@@

\begin{figure}[ht]
    \begin{center}
        \includegraphics[width=0.7\textwidth]{../images/maps.png}
        \caption{Maps component}
        \label{fig:maps}
    \end{center}
\end{figure}
